Dependent Object Types

### 2012-09-06 doc/candidacy/slides.tex
rev
notes
slide numbers, thanks xeno-by

@@

class Library {
  int distance(Graph.Node n1, n1.out.Node n2) { ... }

@@

\begin{frame}{${\nu}Obj$}
A calculus for classes and objects which can have types as members. It can encode:
\begin{itemize}
\item Java's inner classes
\item virtual types
\item family polymorphism
\item essential aspects of ML-like module systems, including
\begin{itemize}
\item sharing constraints
\item higher-order functors
\end{itemize}
\end{itemize}
A basis for unifying concepts  in advaced object and module systems. Connections:
\begin{itemize}
\item Object = Module
\item Object type = Signature
\item Class = Method = Functor
\end{itemize}
\end{frame}

\begin{frame}{${\nu}Obj$: Syntax}
\begin{itemize}
\item terms in ${\nu}Obj$ denote objects or classes; consist of:
\begin{description}[mixin compositions]
\item[variables] $x$
\item[selections] $t.l$
\item[object creations] \mbox{$\newin{x \larrowc t}{u}$}
\item[class templates] $\cls{x: S \sep \tup d}$
\item[mixin compositions] $t \withsub{S} u$
\end{description}
\item a value is a variable or class template
\item a path is a variable followed by a possibly empty sequence of selections
\item types in ${\nu}Obj$ consist of:
\begin{description}[mixin compositions]
\item[singleton types] $p.\type$
\item[type selections] $T\Tsel L$
\item[record types] $\obj{x \sep \tup D}$
\item[compound types] $T \with U$
\item[class types] $\cls{x: S \sep \tup D}$
\end{description}
\end{itemize}
\end{frame}

>>>>

\useoutertheme{infolines}
\setbeamertemplate{headline}{} % removes the headline that infolines inserts
% \setbeamertemplate{footline}{
%   \hfill%
%   \usebeamercolor[fg]{page number in head/foot}%
%   \usebeamerfont{page number in head/foot}%
%   \insertpagenumber\,/\,\insertpresentationendpage\kern1em\vskip2pt%
% }
\setbeamertemplate{footline}{
  \hfill%
  \usebeamercolor[fg]{page number in head/foot}%
  \usebeamerfont{page number in head/foot}%
  \insertpagenumber\kern1em\vskip2pt%
}
\setbeamertemplate{navigation symbols}{}

@@

class Library {
  int distance(Graph.Node n1, n1.out.Node n2)  { ... }
  int distance2(Graph g, g.Node n1, g.Node n2) { ... }

@@

\begin{frame}{${\nu}Obj$}
A calculus for classes and objects which can have types as members. It can encode:
\begin{itemize}
\item Java's inner classes
\item virtual types
\item family polymorphism
\item essential aspects of ML-like module systems, including
\begin{itemize}
\item sharing constraints
\item higher-order functors
\end{itemize}
\end{itemize}
A basis for unifying concepts  in advanced object and module systems. Connections:
\begin{itemize}
\item Object = Module
\item Object type = Signature
\item Class = Method = Functor
\end{itemize}
\end{frame}

\begin{frame}{${\nu}Obj$: Syntax}
\begin{itemize}
\item terms in ${\nu}Obj$ denote objects or classes; consist of:
\begin{description}[mixin compositions]
\item[variables] $x$
\item[selections] $t.l$
\item[object creations] \mbox{$\newin{x \larrowc t}{u}$}
\item[class templates] $\cls{x: S \sep \tup d}$
\item[mixin compositions] $t \withsub{S} u$
\end{description}
\item a value is a variable or class template
\item a path is a variable followed by a possibly empty sequence of selections
\item types in ${\nu}Obj$ consist of:
\begin{description}[mixin compositions]
\item[singleton types] $p.\type$
\item[type selections] $T\Tsel L$
\item[record types] $\obj{x \sep \tup D}$ % explain difference between record and class types?
\item[compound types] $T \with U$
\item[class types] $\cls{x: S \sep \tup D}$
\end{description}
\end{itemize}
\end{frame}
